### 2022-05-10 manuscript.Rmd

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  sensitivity_analysis = FALSE
)

# Options for MCMC sampling when fitting Bayesian multilevel models
n_iter <- 4000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 1000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible

@@

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior"),
  file_refit = brms_file_refit
)
summary(res_prior)
# plot(res_prior)

>>>>

# Re-run steps that take a long time?
run <- list(
  bayesian_models = TRUE,
  sensitivity_analysis = TRUE
)

# Options for MCMC sampling when fitting Bayesian multilevel models
n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 2000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible

@@

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior"),
  file_refit = brms_file_refit
)
summary(res_prior)
# plot(res_prior)
